Data Formatting

### 2021-02-24 scripts/data_format.Rmd
add note about species 32
remove melt function and add as_tibble

Packages
```{r}
library(tidyverse)
library(magrittr)
library(vegan)
library(reshape)
library(here)
```

@@

@@

shannon <- vegan::diversity(abundance_mat, index = "shannon")
shannon <- melt(as.matrix(shannon))
shannon %<>% mutate(siteID = Var1, h = value) %>% dplyr::select(siteID, h)

>>>>

Packages
```{r}
library(tidyverse)
library(magrittr)
library(vegan)
library(here)
```

@@

Note: Species 32 - Hyla avivoca is the bird-voiced tree frog. Data exists for this species' viral load but there is no data regarding its abundance.

@@

shannon <- as_tibble(vegan::diversity(abundance_mat, index = "shannon"),rownames= "siteID")

shannon %<>% mutate(h = value) %>% dplyr::select(siteID, h)
